\documentclass{abrice}

\title{Comp 549: Assignment 5}
\author{Anthony Brice}

\begin{document}
\maketitle

\section{Part 1}

\subsection{Put-That-There Demo, Bolt}

The application's ability to interpret voice and gesture commands is very
impressive, particularly its ability understand pronouns as referent to objects
given through gesture. That said, the interface seems restricted to a fairly
trivial domain.

\subsection{Samsung Gesture Recognition Technology TV Demo At CES 2013}

I found it funny that the reporter had to get out of view of the television's
camera in order for it to recognize the PR rep's hand. It seems that the
technology in the previous video was much more advanced in that regard.

Overall, this demonstration is impressive in that it presents a very practical
domain for the technology presented in the previous video. I'd love to replace
my television remote with voice and gesture commands, and I think it works
because the way in which one uses a television is only minimally interactive.

\subsection{Google's New Finger Control Technology}

I'm a little skeptical about practical applications of this form of
interaction. As Suchman notes, ``designers have long held the view that ideally
a device should be \ldots\ decipherable solely from information provided by the
device itself.'' I imagine with this technology it would be particularly
difficult to convey to a user the ways in which he or she can interact and even
the location within which one interacts with the device. Perhaps my fears will
be shown unfounded if Google can demonstrate that a small vocabulary of gestures
can provide rich interaction with a device, but the video itself didn't
show only real use cases, only target demonstrations.

\section{Part 2}

\subsection{Plans and Situated Actions: The Problem of Human-Machine
  Communication, Suchman}

Suchman's thesis demonstrates quite clearly just how much is still lacking in
the ability humans have to communicate with machines. I find the concept of the
expert system to be a very practical and well thought-out response to the
challenges presented, especially by tying ``the particular problem of designing
a machine that responds appropriately to the actions of a user, to the general
problem of deciding the significance of purposeful action.'' As Suchman's
diagrams demonstrate, the problem is quite non-trivial.

I like that she gives a precise definition of the user's expectations of the
system's response, ``that each system response conveys, either implicitly or
explicitly, an assessment of the last action she has taken and a recommendation
for what to do next.'' I think such strict prescriptions keep her honest in her
evaluation, and do note how much more grounded the idea of the expert system is
compared to something like Licklider's OLIVER\@.

I must admit that before reading the thesis I was among those who dismissed the
``mutual relevance'' of ``research in machine intelligence, and human-machine
communication, on the one hand, and social studies of situated action and
interaction, on the other.''

\subsection{From Turtles to Tangible Programming Bricks: Exploration in Physical
Language Design, McNerney}

While I found all the research described in the paper commendable, I was
especially interested in McNerney's application of functional programming
concepts in his Digital Construction Set. I agree that ``[p]rograms
using streams are naturally concise,'' and its always validating to hear a
prominent researcher say it.

I was initially dismayed that the researchers described in the paper seem to
have dismissed video games entirely from their purview, but considering the
paper was published in 2003 and covers research dating back thirty-five years I
can't say I blame them. \emph{Minecraft} wasn't released until 2009, but it
seems to fit to a tee Papert's ``concept of a \emph{microworld}, a deliberately
simplified computational environment that allows students to explore ideas that
are not normally demonstrable in an average classroom setting.'' I would be very
interested to get McNerney's take on the game's efficacy in teaching children
programming through its integration of Boolean algebra. Considering that so many
children have been taken in by an application that takes the approach of
teaching programming through the low-level language of circuit boards, I wonder
if this might contradict McNerney and the other researchers' assumption that
only allowing programs in a high-level language without branching would ease
learning.

\end{document}
%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
